Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-15 thesis/thesis.tex
thesis: Fix errors estimation

Table \ref{tab:results_melotte_22} shows a summary of Melotte 22 with values taken from different sources and methods:
SIMBAD Astronomical Database - CDS (Strasbourg),
Clusterix+TOPCAT method, and the results obtained for each step of this method (KMeans, DEC and DEC filtered).

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr}\tablefootnote{Results have been taken from \protect\citeA[p.~25. Table A.3. Pleiades]{babusiaux2018gaia}} &
        19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      Clusterix+TOPCAT & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 35.16 & -38.01 $\pm$ 40.16 & 7.23 $\pm$ 2.35 & 1378 \\
      DEC & 23.67 $\pm$ 38.33 & -46.23 $\pm$ 44.54 & 8.04 $\pm$ 2.59 & 878 \\
      \textbf{DEC (filtered)} & 19.50 $\pm$ 8.59 & -44.23 $\pm$ 8.17 & 7.42 $\pm$ 0.1 & 438 \\
    \end{tabular}
    \caption{Parameters shown are proper motion in right ascension and declination, parallax
             with their respective deviations and number of stars corresponding to Melotte 22 data.}
    \label{tab:results_melotte_22}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      \textbf{Clusterix+TOPCAT} & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 35.16 & -38.01 $\pm$ 40.16 & 7.23 $\pm$ 2.35 & 1378 \\
      DEC & 23.67 $\pm$ 38.33 & -46.23 $\pm$ 44.54 & 8.04 $\pm$ 2.59 & 878 \\
      DEC (filtered) & 19.50 $\pm$ 8.59 & -44.23 $\pm$ 8.17 & 7.42 $\pm$ 0.1 & 438 \\
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
      Clusterix+TOPCAT & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
      KMeans & -4.344 $\pm$ 5.670 & 9.507 $\pm$ 7.546 & 2.268 $\pm$ 0.288 & 1542 \\
      DEC & -4.426 $\pm$ 6.529 & 9.952 $\pm$ 8.018 & 2.436 $\pm$ 0.358 & 1532 \\
      \textbf{DEC (filtered)} & -4.502 $\pm$ 4.46 & 10.114 $\pm$ 5.719 & 2.392 $\pm$ 0.135 & 1072 \\
    \end{tabular}
    \caption{NGC 2516 results.}
    \label{tab:results_ngc_2516}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 20.562 & -15.828 $\pm$ 19.152 & 5.394 $\pm$ 0.696 & 629 \\
      DEC & -20.012 $\pm$ 20.657 & -14.742 $\pm$ 17.330 & 4.686 $\pm$ 0.855 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 19.825 & -14.234 $\pm$ 16.388 & 4.719 $\pm$ 0.706 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -10.9737 $\pm$ 0.0064 & -2.9396 $\pm$ 0.0063 & 1.1325 $\pm$ 0.0011 & 1194 \\
      Clusterix+TOPCAT & -10.970 $\pm$ 0.322 & -2.958 $\pm$ 0.327 & 1.142 $\pm$ 0.080 & 649 \\
      KMeans & -8.616 $\pm$ 5.591 & -3.710 $\pm$ 6.067 & 1.196 $\pm$ 0.226 & 1374 \\
      DEC & -8.926 $\pm$ 5.278 & -3.550 $\pm$ 5.425 & 1.144 $\pm$ 0.159 & 1238 \\
      \textbf{DEC (filtered)} & -9.619 $\pm$ 4.112 & -3.317 $\pm$ 3.976 & 1.140 $\pm$ 0.089 & 990 \\
    \end{tabular}
    \caption{NGC 2682 results.}
    \label{tab:results_ngc_2682}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 104.92 $\pm$ 0.12 & -28.00 $\pm$ 0.09 & 21.052 $\pm$ 0.065 & - \\
      Clusterix+TOPCAT & 106.796 $\pm$ 6.229 & -24.870 $\pm$ 5.417 & 21.210 $\pm$ 1.115 & 109 \\
      KMeans & 79.380 $\pm$ 71.691 & -45.314 $\pm$ 73.366 & 20.866 $\pm$ 6.029 & 376 \\
      DEC & 76.463 $\pm$ 72.023 & -43.941 $\pm$ 72.556 & 20.489 $\pm$ 6.138 & 396 \\
      \textbf{DEC (filtered)} & 81.795 $\pm$ 65.626 & -40.049 $\pm$ 55.112 & 19.888 $\pm$ 2.251 & 316 \\
    \end{tabular}
    \caption{Melotte 25 results.}
    \label{tab:results_melotte_25}
  \end{center}
\end{table}

>>>>

Table \ref{tab:results_melotte_22} shows a summary of Melotte 22 with values taken from different sources and methods:
SIMBAD Astronomical Database - CDS (Strasbourg),
Clusterix+TOPCAT method, and the results obtained for each step of this method (KMeans, DEC and DEC filtered).
The errors associated to KMeans and DEC predictions are calculated as the Standard Error $SE = \sigma / \sqrt{N}$,
where $N$ is the number of samples in the selected group.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr}\tablefootnote{Results have been taken from \protect\citeA[p.~25. Table A.3. Pleiades]{babusiaux2018gaia}} &
        19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      Clusterix+TOPCAT & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 0.95 & -38.01 $\pm$ 1.08 & 7.23 $\pm$ 0.06 & 1378 \\
      DEC & 23.67 $\pm$ 1.29 & -46.23 $\pm$ 1.50 & 8.04 $\pm$ 0.09 & 878 \\
      \textbf{DEC (filtered)} & 19.50 $\pm$ 0.41 & -44.23 $\pm$ 0.39 & 7.42 $\pm$ 0.005 & 438 \\
    \end{tabular}
    \caption{Parameters shown are proper motion in right ascension and declination, parallax
             with their respective deviations and number of stars corresponding to Melotte 22 data.}
    \label{tab:results_melotte_22}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      \textbf{Clusterix+TOPCAT} & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 0.95 & -38.01 $\pm$ 1.08 & 7.23 $\pm$ 0.06 & 1378 \\
      DEC & 23.67 $\pm$ 1.29 & -46.23 $\pm$ 1.50 & 8.04 $\pm$ 0.09 & 878 \\
      DEC (filtered) & 19.50 $\pm$ 0.41 & -44.23 $\pm$ 0.39 & 7.42 $\pm$ 0.005 & 438 \\
    \end{tabular}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
      Clusterix+TOPCAT & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
      KMeans & -4.344 $\pm$ 0.14 & 9.507 $\pm$ 0.19 & 2.268 $\pm$ 0.01 & 1542 \\
      DEC & -4.426 $\pm$ 0.17 & 9.952 $\pm$ 0.20 & 2.436 $\pm$ 0.01 & 1532 \\
      \textbf{DEC (filtered)} & -4.502 $\pm$ 0.14 & 10.114 $\pm$ 0.17 & 2.392 $\pm$ 0.004 & 1072 \\
    \end{tabular}
    \caption{NGC 2516 results.}
    \label{tab:results_ngc_2516}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 0.82 & -15.828 $\pm$ 0.76 & 5.394 $\pm$ 0.03 & 629 \\
      DEC & -20.012 $\pm$ 0.69 & -14.742 $\pm$ 0.58 & 4.686 $\pm$ 0.03 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 0.74 & -14.234 $\pm$ 0.61 & 4.719 $\pm$ 0.03 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -10.9737 $\pm$ 0.0064 & -2.9396 $\pm$ 0.0063 & 1.1325 $\pm$ 0.0011 & 1194 \\
      Clusterix+TOPCAT & -10.970 $\pm$ 0.322 & -2.958 $\pm$ 0.327 & 1.142 $\pm$ 0.080 & 649 \\
      KMeans & -8.616 $\pm$ 0.15 & -3.710 $\pm$ 0.16 & 1.196 $\pm$ 0.01 & 1374 \\
      DEC & -8.926 $\pm$ 0.15 & -3.550 $\pm$ 0.15 & 1.144 $\pm$ 0.005 & 1238 \\
      \textbf{DEC (filtered)} & -9.619 $\pm$ 0.13 & -3.317 $\pm$ 0.13 & 1.140 $\pm$ 0.003 & 990 \\
    \end{tabular}
    \caption{NGC 2682 results.}
    \label{tab:results_ngc_2682}
  \end{center}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 104.92 $\pm$ 0.12 & -28.00 $\pm$ 0.09 & 21.052 $\pm$ 0.065 & - \\
      Clusterix+TOPCAT & 106.796 $\pm$ 6.229 & -24.870 $\pm$ 5.417 & 21.210 $\pm$ 1.115 & 109 \\
      KMeans & 79.380 $\pm$ 3.7 & -45.314 $\pm$ 3.8 & 20.866 $\pm$ 0.31 & 376 \\
      DEC & 76.463 $\pm$ 3.6 & -43.941 $\pm$ 3.6 & 20.489 $\pm$ 0.31 & 396 \\
      \textbf{DEC (filtered)} & 81.795 $\pm$ 3.7 & -40.049 $\pm$ 3.1 & 19.888 $\pm$ 0.13 & 316 \\
    \end{tabular}
    \caption{Melotte 25 results.}
    \label{tab:results_melotte_25}
  \end{center}
\end{table}
